Quantifying the home ground advantage

### 2019-04-24 inst/home_advantage.Rmd
typos and clarification

```{r}
for(i in seq_len(nrow(away_games_won))){
  for(j in seq_len(ncol(away_games_won))){
    if(i != j){
      game_winner <- teams[i]
      game_loser  <- teams[j]
      no_of_matches <- away_games_won[i,j] # won with home strength helping
      H[c(game_winner                  )] %<>% inc(no_of_matches)  # won with home ground helping
      H[c(game_winner,game_loser,"home")] %<>% dec(no_of_matches)
    }
  }
}
```

>>>>

```{r}
for(i in seq_len(nrow(away_games_won))){
  for(j in seq_len(ncol(away_games_won))){
    if(i != j){
      game_winner <- teams[i]
      game_loser  <- teams[j]
      no_of_matches <- away_games_won[i,j] # won without the benefit of home strength
      H[c(game_winner                  )] %<>% inc(no_of_matches)  # won without home ground helping...
      H[c(game_winner,game_loser,"home")] %<>% dec(no_of_matches)  # home strength nevertheless on denominator
    }
  }
}
```
